Observed vs. Simulated Year Comparison

### 2022-09-16 03-post-process/output-plots-children/03-fit-to-data.Rmd
Fix header levels in fit-to-data Rmd
Fix issues with file paths in output-plots Rmd

#### Spawn Status Data

@@

#### Mean Length Data {.tabset .tabset-pills}

##### Summer Parr

@@

##### Spring Smolt

@@

```{r pp-check-output, child = "03a-pp-checks.Rmd", eval = model_info$do_pp_check}
```

```{r waic-output, child = "03b-waic.Rmd", eval = model_info$do_lppd}
```

>>>>

### Spawn Status Data

@@

### Mean Length Data {.tabset .tabset-pills}

#### Summer Parr

@@

#### Spring Smolt

@@

```{r pp-check-output, child = "output-plots-children/03a-pp-checks.Rmd", eval = model_info$do_pp_check}
```

```{r waic-output, child = "output-plots-children/03b-waic.Rmd", eval = model_info$do_lppd}
```
